\chapter{Introduction}

Computer science has become one of the most important fields in today’s world due to the rapid digital transformation and the strong technology sector in Germany. Software development and information technologies play an essential role across almost every industry. As a result, computer engineers are expected not only to have solid theoretical knowledge but also practical experience in real-world applications.

For me, applying the theoretical knowledge gained during my studies to real projects has always been of great importance. Germany’s practice-oriented education system and the opportunities offered by THWS were key factors in my decision to study here. Through my internship, I had the opportunity to further develop my technical skills as well as gain valuable insight into the professional working environment in Germany.

\section{Motivation}
During my search for a suitable internship, several factors played an important role in my decision-making process. Gaining technical experience, working within a team under a structured project environment, and improving my personal weaknesses were key criteria for selecting my internship placement. In particular, I aimed to deepen my knowledge of a programming language and further develop my technical skill set.

One aspect that particularly stood out to me at Anevis was the structured way of working, including regular meetings, clearly defined task distribution, and the opportunity to independently complete assigned responsibilities. Another important motivation for me was the chance to adapt to and work within an existing software system. This was especially relevant, as I recognized that integrating into an already established codebase is more challenging than developing a project from scratch.

Overall, this experience represented an important step for me in improving my ability to work in a team, adapt to existing systems, and develop a more disciplined and structured approach to software development.