\chapter{Conclusion}
During this internship, I gained both technical and personal development through hands-on work in a professional software development environment. I was able to strengthen my core programming skills, improve my understanding of development workflows, and become more comfortable working in a team setting.

The experience helped me build a solid foundation in Java, databases such as SQL and MongoDB, and essential tools like Git and Linux. In addition, working with tools such as JFreeChart, JasperSoft, and Atlassian products contributed to my practical understanding of real-world software development processes.

Overall, this internship provided valuable insights into both technical development and workplace practices, and it highlighted areas where I can continue to improve, especially in structured learning and documentation usage.

\section{Learning Outcomes}

\subsection{Soft Skills}
\begin{itemize}
    \item Developed strong self-learning abilities through independent research and problem-solving using real examples.
    \item Improved communication within a team environment by actively participating in meetings and giving/receiving regular feedback.
    \item Gained experience in balancing work, study, and personal life in a structured and sustainable way.
    \item Built a more natural programming mindset by reducing reliance on AI tools and focusing more on understanding fundamentals and reasoning.
\end{itemize}


\subsection{Technical Skills}

\begin{itemize}
    \item Acquired a solid foundation in Java through hands-on development tasks.
    \item Gained good working knowledge of SQL and MongoDB, including writing and optimizing queries.
    \item Strengthened version control practices by regularly using Git in daily workflows.
    \item Gained practical experience working in a Linux-based development environment.
    \item Worked with data visualization and reporting tools such as JFreeChart customization and JasperSoft.
    \item Developed familiarity with Atlassian tools (e.g., Jira, Confluence) in a structured project environment.
    \item Improved proficiency in Microsoft Excel for data handling and reporting tasks.
\end{itemize}

\subsection{Challenges and Areas for Improvement}
\begin{itemize}
    \item Tended to approach learning too quickly and broadly at the beginning, often trying to cover too many topics at once instead of focusing on depth.
    \item At times, skipped onboarding materials and documentation under the assumption that I was already familiar with the content. For example, I did not review certain Confluence resources (such as the OPSDEV folder) in sufficient detail early on, and only started going through them more thoroughly around week 7 of the internship.
\end{itemize}


